Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-05-07 files/Chapter2/generalvibrationmodel.tex
Some local chamges

\subsubsection{Validity of series solution}
Consider the following question: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$? To answer this question, consider the article \cite{CVV18}.

@@

In \cite{CVV18}, the validity of the series solution is proved using the energy norms, where the energy $\mathcal{E}$ a function $u$ given by
\begin{eqnarray}
	\mathcal{E} (t) = \frac{1}{2} b(u(t), u(t)) + \frac{1}{2} c(u'(t), u'(t)). \label{eq:1D_Model:ModalAnalysisEnergy}
\end{eqnarray}

The partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions to Problem GVar.

In \cite{CVV18}, a error function is defined $u^E_N = u - u^N$. Following the initial conditions, $u^E_N = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.

The authors of \cite{CVV18} prove that $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$. Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$.

@@

\subsubsection{Comparison of models}
In this dissertation, we are trying to compare different models for use in applications. Being able to express the solutions of the models as a formal series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.\\

The validity of the formal series solution with initial conditions is required to investigate the vibration of the models. This ensured that if the models are disturbed in the exact same way, the formal series solution is valid, and therefore the comparison can be made.

>>>>

\subsubsection{Validity of series solution}
Consider the following question: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$? To answer this question, we refer to the article \cite{CVV18}.

In article, the validity of the series solution is proved using energy norms, where the energy $\mathcal{E}$ a function $u$ given by
\begin{eqnarray}
	\mathcal{E} (t) = \frac{1}{2} b(u(t), u(t)) + \frac{1}{2} c(u'(t), u'(t)). \label{eq:1D_Model:ModalAnalysisEnergy}
\end{eqnarray}

The authors also prove that for all $t>0$, $\mathcal{E}(t) \leq \mathcal{E}(0)$.

@@

Substitution shows that these partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions to Problem GVar.

The authors then define an error function $u^E_N = u - u^N$. Since both $u$ and $u^N$ satisfies Problem GVar, so does this error function with the following the initial conditions, $u^E_N(0) = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.

Let $\mathcal{E}$ denote the energy of the error function $u^E_N$. Since $\mathcal{E}(t) \leq \mathcal{E}(0)$ for all $t>0$ it follows that, \[||u(t) -  u^N(t)||_V^2 + ||u'(t) - (u^N)'(t)||^2_W \leq ||u_0 - u^N_0||_V^2 + ||u_1 - u^N_1||_W^2. \]

The authors of \cite{CVV18} prove that both $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$. Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$.

@@

\subsubsection{Comparison of models}

In this dissertation, we are trying to compare different models for use in applications. Being able to express the solutions of the models as a formal series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.

The validity of the formal series solution with initial conditions is required to investigate the vibration of the models. This ensured that if the models are disturbed in the exact same way, the formal series solution remains valid, and a fair comparison can be made.
